	I would like to thank my advisor Prof. Robert Likamwa for his continuous support and guidance. He helped me in self realization and made me confidant to work in ambiguities. I would like to thank my mom Sujatha (Kaasu) and dad Peddakapu(Bucchiya Chowdary) for their eternal love and support. I am what I am today because of them. Even though they didn't get to study, they had bigger dreams for me, so spent all their earnings to provide me decent education. I will cherish my grandma and my childhood memories with her. She raised me and never cared anything more than my well being. 
	
	I would like to thank Monish Pabrai and Dakshana, who played a crutial role when I was looking for opportunities and encouraged me by providing free books and excellent teachers, who are the best I have seen so far. I wouldn't have cracked the entrance exams without the training they have provided and certainly helped me in moulding my future. 
	
	I thank my friends Kotta, Palanki, Gadda, Raks, Pathre and Penju for  the moral support whenever needed in US. I would like to thank my flatmates KV, TR, Vivek Rai, and Deshpande, and my friends Druthi, and lab buddies Jinhan, Venky, Siddhanth, Vraj, Alireja, Paul, and Saad. I especially thank Sahab for his willingness to help others. 
	
	I would also like to thank brother Raghu,  cousins Naveen, Chinnu, Lavu, Mahesh, and my dearest sis Reshu, fun cousins Sunny, Teja, Akhi, Nikkhi, and uncle Muralidhar Rao, Rambabu, Srinu, Vijay Babai. I would also like to thank my bava Babby, akka Lakshmi for their love. Most of all I would like to thank Abbu Tataya for his belief in me and supporting me financially. I thank Shanthi pinni and Hari Babi for being supportive to my family during tough times. I would like to thank Richard Hammings, and Richard Feynman being a source of inspiration and I thank myself for being ever curious!
